Modeling Predator Preferences

### 2014-09-11 paper/methods.tex
fix standard errors, to account for correlations among some parameters; information matrix now produced

@@

\subsection*{Assumptions}

Our data collection scheme assumes the following: $1)$ traps independently catch prey that are encountered at a constant rate, $2)$ all traps are equally likely to catch the prey species of interest, $3)$ predators eat, at a constant rate, prey species independently.  Though there exists a non-zero chance that these assumptions are broken, we feel that slight deviations from them will not overtly effect the estimates.

@@

\noindent  Take the expectation of the complete data log-likelihood with respect to $f_{X|Y,Z,\boldsymbol{\lambda},\boldsymbol{\gamma}}(x_{jst})$ to get

>>>>

Our data collection scheme assumes the following: $1)$ traps independently catch prey that are encountered at a constant rate, $2)$ all traps are equally likely to catch the prey species of interest, $3)$ predators eat, at a constant rate, prey species independently, $4)$ predators eat indepedent of each other.  Though there exists a non-zero chance that these assumptions are broken, we feel that slight deviations from them will not overtly effect the estimates.

@@

@@

\noindent The E-step of the EM algorithm is completed by computing the expected value of the complete data log-likelihood with respect to $f_{X|Y,Z,\boldsymbol{\lambda},\boldsymbol{\gamma}}(x_{jst})$ to get
